---
output: github_document
---

# dcflights21

<!-- badges: start -->
[![R-CMD-check](https://github.com/simonpcouch/dcflights21/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/simonpcouch/dcflights21/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

{dcflights21} is an R data-only package supplying data on out-bound flights from airports serving Washington, DC in 2021.

You can install the package with the following lines

```{r, eval = FALSE}
# install.packages("pak")

pak::pak("simonpcouch/dcflights21")
```

# Preview

The package exports one tibble, `dcflights21`, with data on flight departures, weather, airline, airport, and the flown plane. The dataset consists of several different data types with varying degrees of missingness.

```{r}
library(dcflights21)

data(dcflights21)

str(dcflights21)
```

# Data Sources

For the most part, the data in this package can be downloaded, processed, packaged, and documented with the following lines:

```{r, eval = FALSE}
# install.packages("anyflights")

library(anyflights)

dcflights21 <- anyflights(station = c("BWI", "DCA", "IAD"), year = 2021)

as_flights_package("dcflights21")
```

The {anyflights} documentation outlines data sources in detail. Changes to the output of the above lines are reproduced in `data-raw/tidy.R`.
